%Version 3.1 December 2024
% See section 11 of the User Manual for version history
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[pdflatex,sn-mathphys-num]{sn-jnl-modified}% Math and Physical Sciences Numbered Reference Style

%%%% Standard Packages
%%<additional latex packages if required can be included here>

\usepackage{geometry}
\geometry{a4paper, left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm}
\usepackage{graphicx}%
\usepackage{multirow}%
\usepackage{amsmath,amssymb,amsfonts}%
\usepackage{amsthm}%
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
\usepackage{algorithm}%
\usepackage{algorithmic}%
\usepackage{listings}%
\usepackage{float}%
\usepackage{setspace}%
\usepackage{subcaption}%
%%%%

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

\begin{document}

\title{Breaking the Precision Ceiling in Physics-Informed Neural
Networks: A Hybrid Fourier-Neural Architecture for
Ultra-High Accuracy}

\author*[1]{\fnm{Wei Shan} \sur{Lee}}\email{wslee@g.puiching.edu.mo}
\author[1]{\fnm{Chi Kiu Althina} \sur{Chau}}
\author[2]{\fnm{Kei Chon} \sur{Sio}}
\author[1]{\fnm{Kam Ian} \sur{Leong}}

\affil[1]{\orgname{Pui Ching Middle School Macau}, \orgaddress{\street{Edificio Pui Ching, 7A Av. de Horta e Costa}, \city{Macao Special Administrative Region}, \postcode{999078}, \country{People's Republic of China}}}
\affil[2]{\orgname{University of Toronto Mississauga}, \orgaddress{\street{Rm. 809, 85 Wood St.}, \state{Ontario}, \postcode{M4Y 0E8}, \country{Canada}}}

\abstract{Physics-informed neural networks (PINNs) have plateaued at errors of $10^{-3}$-$10^{-4}$ for fourth-order partial differential equations, creating a perceived precision ceiling that limits their adoption in engineering applications. We break through this barrier with a hybrid Fourier-neural architecture for the Euler-Bernoulli beam equation, achieving unprecedented L2 error of $1.94 \times 10^{-7}$—a 17-fold improvement over standard PINNs and 15-500× better than traditional numerical methods. Our approach synergistically combines a truncated Fourier series capturing dominant modal behavior with a deep neural network providing adaptive residual corrections. A systematic harmonic optimization study revealed a counter-intuitive discovery: exactly 10 harmonics yield optimal performance, with accuracy catastrophically degrading from $10^{-7}$ to $10^{-1}$ beyond this threshold. The two-phase optimization strategy (Adam followed by L-BFGS) and adaptive weight balancing enable stable ultra-precision convergence. GPU-accelerated implementation achieves sub-30-minute training despite fourth-order derivative complexity. By addressing 12 critical gaps in existing approaches—from architectural rigidity to optimization landscapes—this work demonstrates that ultra-precision is achievable through proper design, opening new paradigms for scientific computing where machine learning can match or exceed traditional numerical methods.}

\keywords{Physics-informed neural networks, Euler-Bernoulli beam equation, Fourth-order PDEs, Hybrid Fourier-neural architecture, Ultra-precision solutions}

\maketitle

\input{introduction_clean}

\input{methods_clean}

\input{resultsAndDiscussions_clean}

\input{conclusions_clean}

\backmatter

\bmhead{Acknowledgements}

The authors thank Pui Ching Middle School Macau PRC for its kindness in supporting this research project.

\section*{Declarations}

\begin{itemize}
%\item Funding: Not applicable
\item Conflict of interest/Competing interests: The author declares no competing interests.
%\item Ethics approval and consent to participate: Not applicable
\item Consent for publication: All authors have read and approved the final manuscript and agree to its publication.
\item Data availability: The data generated during this study are available from the corresponding author upon reasonable request.
%\item Materials availability: Not applicable
\item Code availability: The code developed for this study is available at \url{https://github.com/weishanlee/PINN-Euler-Bernoulli-Beam}.
\end{itemize}

\input{appendixAIReport_clean}

\bibliography{ref_final}% merged bibliography file

%\input{appendix_clean}

\end{document}
